---
title: "Homework"
author: '18099'
date: "2018"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


#A-2018-09-14
#example 1
```{r}
a<-matrix(1:9,3,3)
b<-matrix(2:4,3,1)
a%*%b
```
#example 2
```{r}
x=rnorm(10)
y=rnorm(10)
plot(x,y,main="example2")
```
#example 3
```{r}
layout(matrix(1:9,3,3))
layout.show(9)

```


#A-2018-9-21
## Question
  A discrete random variable X has probability mass function x

|x|0|1|2|3|4|
  |:--:|:--:|:--:|:--:|:--:|:--:|
  |p(x)|0.1|0.2|0.2|0.2|0.3|

  Use the inverse transform method to generate a random sample of size 1000 from the distribution of X. Construct a relative frequency table and compare the empirical with the theoretical probabilities. Repeat using the R sample function.


## Answer

```{r}
library(ggplot2)
set.seed(123)#guarantee that the program can be repeated with the same result
x <- 0:4#define r.v. x
p <- c(0.1,0.2,0.2,0.2,0.3)#the relative probability of x
cp <- cumsum(p)#cumulative sum of probability
m <- 1000#size of samples
r <- numeric(m)#construct a zero vector with length of 1000
r <- x[findInterval(runif(m),cp)+1]
# Generate 1000 sample from a uniform distribution and find where does every sample fall in the interval of cp.Every interval corresponds a value of random variable x.
table_r <- table(r)
print(table_r)

#theoretical probability
t_p <- p*1000
names(t_p) <- x
print(t_p)#show the theoretical 1000 samples
a <- data.frame(x,freq = c(105,193,205,200,297,100,200,200,200,300),type = rep(c('random sample','theoretical sample'),each = 5))
ggplot(a,aes(x = x ,y =freq ,fill = type))+geom_col(position = 'dodge')
```

Firstly, I use the inverse transform method to generate 1000 samples from distribution x,which is shown as the table. More details can be seen in the comment of the code.

Then I use the "ggplot2" package to create a figure to show the difference of random sample from the distribution x between the sample from theoretical distribution.

As the figure shows, the difference is very tiny with a relatively large sample. So we can regard the inverse transform method as a appoximation to the theoretical distribution.

## Question
Write a function to generate a random sample of size n from the Beta(*a*, *b*) distribution by the acceptance-rejection method. Generate a random sample of size 1000 from the Beta(3,2) distribution. Graph the histogram of the sample with the theoretical Beta(3,2) density superimposed.

## Answer
As known to all, Beta function is defined as $B(a,b)=\int_0^1x^{a-1}(1-x)^{b-1}dx$, and the pdf of Beta distribution is $f(x,a,b)=\frac{1}{B(a,b)}x^{a-1}(1-x)^{b-1}$.
Then I use the acceptance-rejection method to define a function which aims to generate a vector of samples of length n from beta distribution,with parameters a and b.
At last, I make a histogram to confirm that this is a valid function.

```{r}
set.seed(300)
beta_arm <- function(n,a,b){
  beta_pdf <- function(x){
    (1/beta(a,b))*(x)^(a-1)*(1-x)^(b-1)#define the pdf of beta distribution
  }
  j <- 0#the time of iteration
  k <- 0#the available sample
  y <- numeric(n)#a zero vector of length n
  while (k < n){
    u <- runif(1)
    j <- j + 1
    x <- runif(1) #random variate from g
    if ((a-1)*x^(a-2) * (b-1)*(1-x)^(b-2) > u) {
      #accept x
      k <- k + 1
      y[k] <- x
    }
  }
  return(y)
}
sample_beta <- beta_arm(1000,3,2)#record the sample
head(sample_beta,20)
sample_beta_theo <- rbeta(1000,3,2)#generate the sample by using the function "rbeta"
data_beta <- data.frame(sample = c(sample_beta,sample_beta_theo),class = rep(c('empirical','theoretical'),each = 1000))#construst a data frame in order to generate a figure
ggplot(data_beta,aes(x = sample,fill = class))+geom_histogram(position="identity", alpha=0.5)
```

## Question
Simulate a continuous Exponential-Gamma mixture. Suppose that the rate parameter $\Lambda$ has $Gamma(r,\beta)$ distribution and $Y$ has $Exp(\lambda)$ distribution. That is, $(Y|\Lambda=\lambda)~f_Y(y|\lambda)=\lambda e-\lambda y$. Generate 1000 random observations from this mixture with $r=4$ and $\beta=2$ .

## Answer
Firstly, I define two parameters of gamma distribution.Then I use this particular gamma distribution to generate 1000 samples, which are the parameter lambda of exponential distribution. Next, I use the function "rexp" generating 1000 samples x from the exponential distribution. Lastly, I plot the histogram of x.
```{r}
set.seed(100)
n <- 1000
r <- 4
beta <- 2#define the parameters
lambda <- rgamma(n, r, beta)#generate the random sample from the gamma distribution with r=4, beta=2
x <- rexp(n, lambda)
head(x,30)#list the first 30 samples
x_data <- data.frame(x1 = x)
ggplot(x_data,aes(x = x1))+geom_histogram(fill = 'skyblue',alpha =0.7,binwidth = 0.4)
```






#A-2018-09-28


#Answer of 5.4
  Since the Beta(3,3) cdf is $$F(x)=\int_{0}^{x}\dfrac{1}{beta(3,3)}t^2(1-t)^2dt=E[g(X)]$$,where $g(x)=xt^2(1-t)^2/beta(3,3),X\sim U(0,1)$, So we have the function
```{r}
MC_Beta<-function(x)
{
  m<-1e5
  y<-runif(m,min=0,max=x)
  F_beta_hat<-mean(x*y^2*(1-y)^2/beta(3,3))
  return(signif(F_beta_hat,4))
}
```
If we choose $x=0.1,\cdots,0.9$,use the function above and compare it with values return from pbeta
```{r}
pbeta_1<-function(x)
{
  return(pbeta(x,3,3))
}
x=seq(0.1,0.9,0.1)
cdf=sapply(x,MC_Beta)
est_cdf=sapply(x,pbeta_1)
A=signif(rbind(x,cdf,est_cdf),3)
print(A)
```
# Answer of 5.9
If X have a Rayleigh distribution, then it gives the cdf of X
$$F(x)=1-e^{-x^2/(2\sigma^2)}, \ x\geq0$$
  $$x=\sqrt{-2\sigma^2log(1-y)},\ 0 \leq y \leq 1$$
  Thus we can gennerate samples from
$$X=\dfrac{\sqrt{-2\sigma^2log(1-U)}+\sqrt{-2\sigma^2log(U)}}{2},U\sim U(0,1)$$
  We have the function
```{r}
sample_Ray<-function(m,sigma)  ##X/2+X'/2
{
  x=runif(m)
  g=sqrt(-2*sigma^2*log(1-x))/2+sqrt(-2*sigma^2*log(x))/2
  return(g)
}
Asample_Ray<-function(m,sigma)  ##X1/2+X2/2
{
  x1=runif(m)
  x2=rinif(m)
  g=sqrt(-2*sigma^2*log(1-x1))/2+sqrt(-2*sigma^2*log(1-x2))/2
  return(g)
}

```


#Answer of 5.13

We choose these two importance functions:
  $$f_1(x)=e^{1/2}xe^{-x^2/2},1<x<\infty$$
  $$f_2(x)=\dfrac{1}{\sqrt{2\pi}}e^{-x^2/2},-\infty < x < \infty$$
  for $f_1(x)$
  $$F_1(x)=1-e^{1/2-x^2/2}$$
  So we can generate samples of $f_1(x)$ from
$$x=\sqrt{1-2log(1-u)} \,\ u \sim U(0,1)$$
  For $f_2(x)$, since it is normal density function, we can generate samples by function rnorm directly.
```{r}
m=1e5
g<-function(x)
{
  x^2*exp(-x^2/2)/sqrt(2*pi)*(x>1)
}

u=runif(m)   ##f_1
x=sqrt(1-2*log(1-u))
fg=g(x)/(exp(1/2)*x*exp(-x^2/2))
MC_1=sd(fg)

x=rnorm(m)  ##f_2
fg=sqrt(2*pi)*g(x)/exp(-x^2/2)
MC_2=sd(fg)
se=c(MC_1,MC_2)
print(se)  ##output the sd of f_1 and f_2
```
From the result,we can see that $f_1(x)$ produce smaller variance.


##Answer of 5.14
As shown in Answer of 5.13, we choose the important function as
$$f_1(x)=e^{1/2}xe^{-x^2/2},1<x<\infty$$
  Thus,after generate m samples we have
```{r}
m=1e5
g<-function(x)
{
  x^2*exp(-x^2/2)/sqrt(2*pi)*(x>1)
}

u=runif(m)   ##f_1
x=sqrt(1-2*log(1-u))
fg=g(x)/(exp(1/2)*x*exp(-x^2/2))
theta_hat=mean(fg)
print(theta_hat)
```
It shows the result.


#A-2018-10-12

#Answer of 6.9
  To estimate the mean,median and deciles , we generate m replicates $T^{(j)}$ by n samples from the distrubution of X.

```{r}
n=20
m=1000
Gi_sam1<-numeric(m)
Gi_sam2<-numeric(m)
Gi_sam3<-numeric(m)
for(i in 1:m)
{
  x<-sort(rlnorm(n,0,1))
  y<-sort(runif(n,0,1))
  z<-sort(rbinom(n,1,0.5))
  J=2*seq(1:n)-n-1
  Gi_sam1[i]=(J%*%x)/(n^2*mean(x))
  Gi_sam2[i]=(J%*%y)/(n^2*mean(y))
  Gi_sam3[i]=(J%*%z)/(n^2*mean(z))
}
log_norm<-c(mean(Gi_sam1),median(Gi_sam1),quantile(Gi_sam1,seq(0,1,0.1)))
unif_norm<-c(mean(Gi_sam2),median(Gi_sam1),quantile(Gi_sam2,seq(0,1,0.1)))
Bern_norm<-c(mean(Gi_sam2),median(Gi_sam1),quantile(Gi_sam3,seq(0,1,0.1)))
A=signif(rbind(log_norm,unif_norm,Bern_norm),3)
colnames(A)=c("mean","median",names(quantile(Gi_sam1,seq(0,1,0.1))))
print(A)

```

Density histograms are shown below.


```{r echo=FALSE}
hist(Gi_sam1,prob=TRUE,main="replicates for lognorm")
hist(Gi_sam2,prob=TRUE,main="replicates for uniform")
hist(Gi_sam3,prob=TRUE,main="replicates for Bernoulli")
```


#Answer of 6.10
With m in a large number, we have the asymptotic distribution about G
$$\frac{\sqrt{m}(\hat G -\gamma)}{\sigma} \sim N(0,1)$$
  a 95% confidence interval for $gamma$is given by
$$\left[\hat G- \frac{u_{0.975}\sigma}{\sqrt{m}} , \hat G +\frac{u_{0.975}\sigma}{\sqrt{m}}\right]$$
  where u denote fractile of standardized normal distribution.


```{r}
n=30
m=100
alpha=0.025
Gi_sam1=numeric(m)
UCL_low<-numeric(1000)
UCL_upp<-numeric(1000)
Mean<-numeric(1000)
for(k in 1:1000)
{ for(i in 1:m) #generate m replitcates
{
  x<-sort(rlnorm(n,0,1))
  J=2*seq(1:n)-n-1
  Gi_sam1[i]=(J%*%x)/(n^2*mean(x))
}

  UCL_low[k]<-  mean(Gi_sam1)-qnorm(1-alpha)*sd(Gi_sam1)/sqrt(m)
  UCL_upp[k]<-  mean(Gi_sam1)+qnorm(1-alpha)*sd(Gi_sam1)/sqrt(m)
  Mean[k]<-mean(Gi_sam1)
}
fin_mean<-mean(Mean)
k=sum(UCL_low<fin_mean & UCL_upp>fin_mean)
mean1<-k/1000
```

From the result, we kanow that its coverage rate is
```{r echo=FALSE}
mean1
```
it is close to 95%.

#Answer of 6.B
Setting $\rho$ as serval value from 0.1 to 1,we calulate their power and plot it in a graph.

```{r}
library(MASS)
m=1000
n=200
ratio<-matrix(0,3,10)
for(j in 1:10)
{
  mean<-c(0,1)
  sigma=matrix(c(1,j/20,j/20,1),2,2)
  p_pearson<-numeric(m)
  p_Spearman<-numeric(m)
  p_Kendall<-numeric(m)
  for(i in 1:m)
  {
    sample=mvrnorm(n,mean,sigma)
    x=sample[,1]
    y=sample[,2]
    test1<-cor.test(x,y,method="pearson")
    test2<-cor.test(x,y,method="kendall")
    test3<-cor.test(x,y,method="spearman")
    p_pearson[i]<-test1$p.value
    p_Spearman[i]<-test2$p.value
    p_Kendall[i]<-test3$p.value
  }

  ratio[,j]=c(mean(p_pearson<0.05),mean(p_Spearman<0.05),mean(p_Kendall<0.05))
}
rownames(ratio)<-c("pearson","speqrman","Kendall")
print(ratio)
plot((1:10)/20,ratio[1,],type="l",col="RED",main="power of three method")
lines((1:10)/20,ratio[2,],type="l",col="BLACK")
lines((1:10)/20,ratio[3,],type="l",col="YELLOW")
```

From the graph, red line meaning "pearson",black meaning speqrman and yellow meaning Kendall, we know that the correlation test based on $\rho_{s}$(Speqrman) and $\tau$(Kendall) are less powerful than the correlation test based on $\rho$.
For X,Y are dependent,we have the code similiar with above.

```{r}
library(MASS)
m=1000
n=200
mean<-c(0,1)
sigma=matrix(c(1,0,0,1),2,2)
p_pearson<-numeric(m)
p_Spearman<-numeric(m)
p_Kendall<-numeric(m)
for(i in 1:m)
{
  sample=mvrnorm(n,mean,sigma)
  x=sample[,1]
  y=sample[,2]
  test1<-cor.test(x,y,method="pearson")
  test2<-cor.test(x,y,method="kendall")
  test3<-cor.test(x,y,method="spearman")
  p_pearson[i]<-test1$p.value
  p_Spearman[i]<-test2$p.value
  p_Kendall[i]<-test3$p.value
}

ratio=c(mean(p_pearson<0.05),mean(p_Spearman<0.05),mean(p_Kendall<0.05))
names(ratio)<-c("peason","Speqrman","Kendall")
print(ratio)
```

As shown from the result,at least one of the nonparaments test have better empirical power than correlation test.

#A-2018-11-02
#Question 7.1
  Compute a jackknife estimate of the bias and the standard error of the correlation statistic in Example 7.2

#Answer of 7.1
Delete $j_{th}$ samples to obtain n replitates, which are used to estimating.The code is shown below.
```{r}
library(bootstrap)
n=length(law$GPA)
theta.hat<-cor(law$LSAT,law$GPA)
theta.jack<-numeric(n)
for(i in 1:n)      #leave one out
{
  theta.jack[i]<-cor(law$LSAT[-i],law$GPA[-i])
}
bias.jack<-(mean(theta.jack)-theta.hat)*(n-1)
se.jack<-sqrt((n-1)/n*sum((theta.jack-mean(theta.jack))^2))
round(c(original=theta.hat,bias=bias.jack,se=se.jack),3)
```

#Question 7.5
Refer to Exercise 7.4. Compute 95% bootstrap confidence intervals for the
mean time between failures $1/\lambda$ by the standard normal, basic, percentile,
and BCa methods. Compare the intervals and explain why they may differ.

#Answer of 7.5
Its known that wth n observations the MLE of $1/\lambda$ is $\overline X$.Here is the code for confidence intervals.
```{r}
library(boot)
hour<-aircondit
B=200     #number of repicates
data<-hour
theta.boot<-function(data,i) #compute statisic
{
  mean(data[i,])
}
boot.obj<-boot(data,statistic = theta.boot,R=2000)
```
the mean and sd of $1/\lambda$ is shown below.
```{r}
print(boot.obj)
```
And confidence intervals for differents method is shown below.
```{r}
print(boot.ci(boot.obj,type=c("basic","norm","perc","bca")))
```

#Question 7.8
Refer to Exercise 7.7. Obtain the jackknife estimates of bias and standard
error of $\hat \theta$.

#Answer of 7.8
We leave one row put form the score matrix to obtain the jackknife eatimates.
```{r}
n=nrow(scor)
theta.an<-function(x) #compute theta
{
  eigen(x)$values[1]/sum(eigen(x)$values)
}
theta.hat1<-theta.an(var(scor))
theta.jack1<-numeric(n)
for(i in 1:n)
{
  theta.jack1[i]<-theta.an(var(scor[-i,]))
}
bias.jack1<-(mean(theta.jack1)-theta.hat1)*(n-1)
se.jack1<-sqrt((n-1)/n*sum((theta.jack1-mean(theta.jack1))^2))
round(c(original=theta.hat1,bias=bias.jack1,se=se.jack1),5)
```

It can be learn form above that the jackknife of bias and standard error of $\hat \theta$ is 0.00107 and 0.04955.


#Queation 7.11
In Example 7.18, leave-one-out (n-fold) cross validation was used to select the
best fitting model. Use leave-two-out cross validation to compare the models.

#Answer of 7.11
Follow the code in  Example 7.18,we have
```{r}
library(DAAG)
attach(ironslag)
n=length(magnetic)
e1<-e2<-e3<-e4<-numeric()
#leave-two-out

for(k in 1:(n-1))
{ l=k+1
y=magnetic[c(-k,-l)]
x=chemical[c(-k,-l)]

J1<-lm(y ~ x)
yhat_a1<-J1$coef[1] + J1$coef[2]*chemical[k]

yhat_b1<-J1$coef[1] + J1$coef[2]*chemical[l]
e1<-c(e1,magnetic[k]-yhat_a1)
e1<-c(e1,magnetic[l]-yhat_b1)

J2<-lm(y ~ x+I(x^2))
yhat_a2<-J2$coef[1] + J2$coef[2]*chemical[k]+J2$coef[3]*chemical[k]^2
yhat_b2<-J2$coef[1] + J2$coef[2]*chemical[l]+J2$coef[3]*chemical[l]^2
e2<-c(e2,magnetic[k]-yhat_a2)
e2<-c(e2,magnetic[l]-yhat_b2)


J3<-lm(log(y) ~ x)
logyhat_a3<-J3$coef[1] + J3$coef[2]*chemical[k]
logyhat_b3<-J3$coef[1] + J3$coef[2]*chemical[l]
e3<-c(e3,magnetic[k]-exp(logyhat_a3))
e3<-c(e3,magnetic[l]-exp(logyhat_b3))

J4<-lm(log(y) ~ log(x))
logyhat_a4<-J4$coef[1] + J4$coef[2]*log(chemical[k])
logyhat_b4<-J4$coef[1] + J4$coef[2]*log(chemical[l])
e4<-c(e4,magnetic[k]-exp(logyhat_a4))
e4<-c(e4,magnetic[l]-exp(logyhat_b4))
}
c(mean(e1^2),mean(e2^2),mean(e3^2),mean(e4^2))


```
Obviously, the second model have the lower errors than the other models.


#A-2018-11-16

##Exercise 8.1
  Implement the two-sample Cramer-von Mises test for equal distributions as a permutation test. Apply the test to the data in Examples 8.1 and 8.2.

##Answer
X and Y are independent random samples form F and G.
$$F = G \ vs \ F \neq G$$
  Obtained from Google, the function "CvM.test" in the packsge "RVAideMemoire" is uesed to compute Cramer-vom Mises statistic. Thus We write a function to compute the p-value with data x and y provided.

```{r}
CVM<-function(x,y){
  N=999#permutation numbers
  n<-length(x);
  m<-length(y);
  f<-ecdf(x);
  g<-ecdf(y);
  z<-c(x,y);
  t<-numeric(N);
  t0<-m*n/(m+n)^2*(sum((f(x)-g(x))^2)+sum((f(y)-g(y))^2));
  for(i in 1:N){
    k<-sample(length(z),size=n,replace = FALSE);
    x1<-z[k];
    y1<-z[-k];
    f1<-ecdf(x1);
    g1<-ecdf(y1);
    t[i]<-m*n/(m+n)^2*(sum((f1(x)-g1(x))^2)+sum((f1(y)-g1(y))^2))
  }
  p <- mean(c(t0,t) >= t0)
  return(p)
}

```

Applying thos function to the data in Example 8.1.
```{r}
attach(chickwts)
x <- sort(as.vector(weight[feed == "soybean"]))
y <- sort(as.vector(weight[feed == "linseed"]))
fin <- CVM(x,y)
fin
detach(chickwts)
```
Clearly, the result  shows that the null hypothesis is not rejected, that is $F = G$.

##Question
Design experiments for evaluating the performance of the NN,
energy, and ball methods in various situations

##Answer
We write all these function and change the data.

1:Unequal variances and equal expectations

```{r}
set.seed(1)
##install.packages("RANN")
##install.packages("energy")
##install.packages("Ball")
library(RANN)
library(boot)
library(energy)
library(Ball)

m <- 50
k<-3
p<-2
n1 <- n2 <- 50
R<-999
n <- n1+n2
N = c(n1,n2)

Tn <- function(z, ix, sizes,k)  {
  n1 <- sizes[1]
  n2 <- sizes[2]
  n <- n1 + n2
  if(is.vector(z)) z <- data.frame(z,0)
  z <- z[ix, ]
  NN <- nn2(data=z, k=k+1)
  block1 <- NN$nn.idx[1:n1,-1]
  block2 <- NN$nn.idx[(n1+1):n,-1]
  i1 <- sum(block1 < n1 + .5); i2 <- sum(block2 > n1+.5)
  (i1 + i2) / (k * n)
}

eqdist.nn <- function(z,sizes,k){
  boot.obj <- boot(data=z,statistic=Tn,R=R,sim = "permutation", sizes = sizes,k=k)
  ts <- c(boot.obj$t0,boot.obj$t)
  p.value <- mean(ts>=ts[1])
  list(statistic=ts[1],p.value=p.value)
}

p.values <- matrix(NA,m,3)
for(i in 1:m){
  x <- matrix(rnorm(n1*p,mean = 1,sd = 0.6),ncol=p);
  y <- matrix(rnorm(n2*p,mean = 1,sd = 0.85),ncol=p);
  z <- rbind(x,y)
  p.values[i,1] <- eqdist.nn(z,N,k)$p.value
  p.values[i,2] <- eqdist.etest(z,sizes=N,R=R)$p.value
  p.values[i,3] <- bd.test(x=x,y=y,R=999,seed = i*12)$p.value
}

alpha <- 0.1;
pow1 <- colMeans(p.values<alpha)
print(pow1)
```
2:Unequal variances and unequal expectations
```{r}
set.seed(1)
p.values <- matrix(NA,m,3)
for(i in 1:m){
  x <- matrix(rnorm(n1*p,mean = 0.4,sd = 0.6),ncol=p);
  y <- matrix(rnorm(n2*p,mean = 0.5,sd = 0.85),ncol=p);
  z <- rbind(x,y)
  p.values[i,1] <- eqdist.nn(z,N,k)$p.value
  p.values[i,2] <- eqdist.etest(z,sizes=N,R=R)$p.value
  p.values[i,3] <- bd.test(x=x,y=y,R=999,seed = i*12)$p.value
}
alpha <- 0.1;
pow2<- colMeans(p.values<alpha)
print(pow2)
```
3:Non-normal distributions: t distribution with 1 df (heavy-tailed distribution),
bimodeldistribution (mixture of two normal distributions)
```{r}
set.seed(1)
p.values <- matrix(NA,m,3)
for(i in 1:m){
  # t distribution with 1 df (heavy-tailed distribution)
  x <- matrix(rt(n1*p,df = 1),ncol=p);
  #bimodel distribution (mixture of two normal distributions)
  y <- cbind(rnorm(n2,mean = 0.4),rnorm(n2,mean = 0.5));
  z <- rbind(x,y)
  p.values[i,1] <- eqdist.nn(z,N,k)$p.value
  p.values[i,2] <- eqdist.etest(z,sizes=N,R=R)$p.value
  p.values[i,3] <- bd.test(x=x,y=y,R=999,seed = i*12)$p.value
}
alpha <- 0.1
pow3 <- colMeans(p.values<alpha)
print(pow3)
```
4:Unbalanced samples


```{r}
set.seed(1)
p.values <- matrix(NA,m,3)
for(i in 1:m){
  x <- c(rnorm(n1,mean = 1,sd = 1))
  y <- c(rnorm(n2,mean = 2,sd = 2))
  z <- c(x,y)
  p.values[i,1] <- eqdist.nn(z,N,k)$p.value
  p.values[i,2] <- eqdist.etest(z,sizes=N,R=R)$p.value
  p.values[i,3] <- bd.test(x=x,y=y,R=999,seed = i*12)$p.value
}
alpha <- 0.1
pow4 <- colMeans(p.values<alpha)
print(pow4)
```


##Exercise 9.3
Use the Metropolis-Hastings sampler to generate random variables from a standard Cauchy distribution. Discard the first 1000 of the chain, and compare the deciles of the generated observations with the deciles of the standard
Cauchy distribution (see qcauchy or qt with df=1). Recall that a Cauchy($\theta$, $\eta$) distribution has density function
$$f(x)=\dfrac{1}{\theta \pi (1+[(x-\eta)/\theta]^2)}, -\infty <  x < \infty ,\theta > \ 0$$

  The standard Cauchy has the Cauchy($\theta$ = 1, $\eta$ = 0) density.

##Answer
Consider $N(X_t,\sigma^2)$ as the proposal diatribution.
```{r}
f <- function(x,theta,eta)
{
  stopifnot(theta > 0)
  return(1/(theta*pi*(1 + ((x-eta)/theta)^2)))
}
m=5000
theta=1
eta=0
sigma <- 1
x <- numeric(m)
x[1] <- rnorm(1, 0, sigma)
k=0
u <- runif(m)

for(i in 2:m)
{
  xt <- x[i-1]
  y<- rnorm(1, mean = xt, sd = sigma)
  num <-f(y,theta,eta) *dnorm(xt, mean = y, sd = sigma)
  den <-f(xt, theta, eta) * dnorm(y, mean = xt, sd = sigma)
  if(u[i] <= num/den) x[i] <- y
  else{
    x[i]<-xt
    k=k+1
  }
}
print(k/m)

```
The rejection rate is `r k/m`
```{r}
b0=1001
index=b0:m
y=x[index]
plot(y~index , type="l", main="",ylab="x")
```

Compare deciles with the theoretical Cauchy(0,1)
```{r}
p=seq(0.1,0.9,0.1)
round( rbind(quantile(y,p), qcauchy(p)),3)

```
The histgram of the chain is shown below.
```{r}
hist(y,prob=T,main='',xlab='x',breaks=50)
xarg=seq(min(y),max(y),0.1)
lines(xarg,f(xarg,theta,eta))
```



## Exercise 9.6
Rao [220, Sec. 5g] presented an example on genetic linkage of 197 animals in four categories (also discussed in [67, 106, 171, 266]). The group sizes are Assume that the probabilities of the corresponding multinomial distribution are
$$\left( 1/2 +\theta/4, (1- \theta)/4, (1-\theta)/4,\theta/4\right)$$
  Estimate the posterior distribution of $\theta$ given the observed sample, using one
of the methods in this chapter.

##Answer
```{r}
set.seed(906)

f <- function( theta,x )  {
  if (theta<0 || theta>1 ) return (0)
  (2+theta)^x[1] * (1-theta)^(x[2]+x[3]) * theta^x[4]
}
xdata = c( 125, 18, 20, 34 )
m = 10000
th = numeric(m)
th[1] = runif(1)
k = 0
u = runif(m)

for (t in 2:m) {
  xt = th[t-1]
  alph = xt/(1-xt)
  y <- rbeta(1, shape1=alph, shape2=1 )
  numer = f( y,xdata ) * dbeta( xt, y/(1-y), 1)
  denom = f( xt,xdata ) * dbeta( y, alph, 1)
  if ( u[t] <= numer/denom )
    th[t] = y else {
      th[t] = th[t-1]
      k = k + 1
    }
}
```
Thus,the estimation of $\theta$ is
```{r}
theta.hat = mean( th[2001:m] )
print(theta.hat)
```



It can be seen that the value of $\hat R$ converage finally.

#A-2018-11-23

##Exercise11.4
Find the intersection points A(k) in $(0,\sqrt(k)$ of the curse
 $$S_{k-1}(a)=1-t_{k-1}(\sqrt(a^2(k-1)/(k-a^2)))$$
  and
 $$S_{k}(a)=1-t_{k}(\sqrt(a^2k/(K+1-a^2)))$$
for k=4:25,100,500,1000.
##Answer
Since
$$S_{k-1}(a)=1-t_{k-1}(\sqrt(a^2(k-1)/(k-a^2)))$$
$$S_{k}(a)=1-t_{k}(\sqrt(a^2k/(K+1-a^2)))$$
where $t_{k}()$ means distribution function of student t. So it equals to find points such that
$$f(a)=t_{k-1}(\sqrt(a^2(k-1)/(k-a^2)))-t_{k}(\sqrt(a^2k/(k+1-a^2)))=0$$
```{r}
ft<-function(a,df){
s1=pt(q=sqrt(a^2*(df-1)/(df-a^2)),df=(df-1),lower =   FALSE)
s2=pt(q=sqrt(a^2*df/(df+1-a^2)),df=df,lower= FALSE)
return(s1-s2)
 }
 kt=c(4:25,100,500,1000)
out=numeric(length(kt))
for(i in 1:length(kt))
{
out[i]=uniroot(ft,lower = 0.001,upper =2,df=kt[i])$root
}
rbind(kt,out)
```

#A-2018-12-7

##Exercise 3(Page 204)
  Use both for loops and lapply() to fit linear models to the
mtcars using the formulas stored in this list:

##Answer

```{r}
attach(mtcars)
xt<-list(disp,I(1/disp),disp+wt,I(1/disp)+wt)
##for loop
lm1<-list()
for(i in seq_along(xt)){
  lm1[[i]]<-lm(mpg~xt[[i]])
}
lm1
##lapply
lm2<-lapply(xt,function(x) lm(mpg~x))
lm2
detach(mtcars)
```

##Exercise 4(Page 204)

Fit the model mpg ~ disp to each of the bootstrap replicates
of mtcars in the list below by using a for loop and lapply().
Can you do it without an anonymous function?

#Answer
```{r}
bootstraps <- lapply(1:10, function(i) {
  rows <- sample(1:nrow(mtcars), rep = TRUE)
  mtcars[rows, ]
})
##lappply
lm3<-lapply(bootstraps, function(x) lm(x$mpg~x$disp))
lm3
##for loop
lm4<-list()
for(i in seq_along(bootstraps)){
  lm4[[i]]<-lm(bootstraps[[i]]$mpg~bootstraps[[i]]$disp)
}
lm4
```

##Exercise 5(Page 204)
For each model in the previous two exercises, extract R2 using the function below.


##Answer
```{r}
##Exercise 3
sapply(lm1,function(mod) summary(mod)$r.squared)
sapply(lm2,function(mod) summary(mod)$r.squared)
##Exercise 4
sapply(lm3,function(mod) summary(mod)$r.squared)
sapply(lm4,function(mod) summary(mod)$r.squared)
```

##Exercise 3(Page 213)
The following code simulates the performance of a t-test for non-normal data. Use sapply() and an anonymous function to extract the p-value from every trial.

##Answer
```{r}
trials <- replicate(
  100,
  t.test(rpois(10, 10), rpois(7, 10)),
  simplify = FALSE
)

sapply(trials,function(x) x$p.value)
```

#A-2018-12-14

##Question 4
  Make a faster version of chisq.test() that only computes the chi-square test statistic when the input is two numeric vectors with no missing values. You can try simplifying chisq.test() or by coding from the mathematical definition

##Answer
```{r}
options(warn=-1)
set.seed(123)
my_chi<-function(x,y)
{
  if (length(x) != length(y))
    stop("'x' and 'y' must have the same length")
  OK <- complete.cases(x, y)
  x <- factor(x[OK])
  y <- factor(y[OK])
  if ((nlevels(x) < 2L) || (nlevels(y) < 2L))
    stop("'x' and 'y' must have at least 2 levels")
  x <- table(x, y)
  p = rep(1/length(x), length(x))
  p <- p/sum(p)
  n<-sum(x)
  E <- n * p
  V <- n * p * (1 - p)
  STATISTIC <- sum((x - E)^2/E)
  STATISTIC
}

x<-runif(10)
y<-runif(10)

my_chi(x,y)
chisq.test(x,y)$statistic

library(microbenchmark)
microbenchmark(
  my_chi(x,y),
  chisq.test(x,y)$statistic
)
```
It can be seen that "my_chi" is much faster than "chisq.test" as twice.


##Question 5
Can you make a faster version of table() for the case of an input of two integer vectors with no missing values? Can you use it to speed up your chi-square test?


##Answer

```{r}
options(warn=-1)
my_table<-function(x,y){
  args<-list(x,y)
  bin <- 0L
  lens <- NULL
  dims <- integer()
  pd <- 1L
  dn <- NULL
  for (a in args) {

    fact.a <- is.factor(a)
    if (!fact.a) {
      a0 <- a
      a <- factor(a)
    }
    ll <- levels(a)
    a <- as.integer(a)
    nl <- length(ll)
    dims <- c(dims, nl)
    if (prod(dims) > .Machine$integer.max)
      stop("attempt to make a table with >= 2^31 elements")
    dn <- c(dn, list(ll))
    bin <- bin + pd * (a - 1L)
    pd <- pd * nl
  }
  bin <- bin[!is.na(bin)]
  if (length(bin))
    bin <- bin + 1L
  y <- array(tabulate(bin, pd), dims, dimnames = dn)
  class(y) <- "table"
  y
}


library(microbenchmark)
x<-1:4
y<-2:5
my_table(x,y)
table(x,y)
microbenchmark(
  my_table(x,y),
  table(x,y)
)

```

It can be seen the function "my table"" is a little faster than "table". Apply this to "my_chi"
to speed up my chi-square test.
```{r}
options(warn=-1)
myy_chi<-function(x,y)
{
  if (length(x) != length(y))
  stop("'x' and 'y' must have the same length")
  OK <- complete.cases(x, y)
  x <- factor(x[OK])
  y <- factor(y[OK])
  if ((nlevels(x) < 2L) || (nlevels(y) < 2L))
  stop("'x' and 'y' must have at least 2 levels")
  x <- my_table(x,y)
  p = rep(1/length(x), length(x))
  p <- p/sum(p)
  n<-sum(x)
  E <- n * p
  V <- n * p * (1 - p)
  STATISTIC <- sum((x - E)^2/E)
  STATISTIC
}

x<-runif(10)
y<-runif(10)

microbenchmark(
myy_chi(x,y),
my_chi(x,y),
chisq.test(x,y)$statistic
)


```
Surprsingly, using "my_table" makes chisqusre test faster, although quite a little bit.
















